---
output: pdf_document
---

#Bayesian Model Averaging for Simulated Impression Change Equations
**Mao Hu**

```{r, include=FALSE}
source("simulation.R")
```

##Introduction



##Simulating Data



**Figure 1: Plot of simulation model coefficients** 

```{r, echo=FALSE, fig.width=6}
ggplot(coefficients, aes(x = index, y = sim.B, label=rownames(coefficients), size = 5, alpha = 0.4)) + geom_point() + geom_text(size = 5, y = sim.B + 0.025) + xlim(c(-5,70)) + theme(text=element_text(size=12),legend.position="none") + ylab("Coefficient") 
```


**Figure 2: Correlation plots**
*Simulated data (left) and Duke '10 (right)*

```{r, echo = FALSE, fig.width=6, fig.height=3}
par(mfcol=c(1,2))
corrplot(cor(sim.X1.design.dataframe[,c("ae","ap","aa","be","bp","ba","oe","op","oa")]))
corrplot(cor(duke10[,c("ae","ap","aa","be","bp","ba","oe","op","oa")]))
```

##Results


**Table 1: Variables identified from training set, by procedure **

*Where the simulation model has 10 true predictors, out of 63 total*  

|Procedures | True positives | False positives | True negatives | False negatives | Sensitivity | Specificity |
|---------- | -------------- | --------------- | ---------------| --------------- | ----------- | ----------- |
|stepwise   | 9              | 15              | 38             | 1               | 0.9         | 0.72        |
|BMA        | 6              | 2               | 51             | 4               | 0.6         | 0.96        |
|ANOVA      | 4              | 1               | 52             | 6               | 0.4         | 0.98        |



**Table 2: Mean square prediction error on test set (n=500)**  

| Procedures         | MSE    |
| ------------------ | ------ |
| stepwise           | 0.532  |
| BMA median model   | 0.509  |
| dichotomized ANOVA | 0.509  |


